A pipeline to analyse time-course gene expression data

### 2020-07-15 scripts/manuscript.Rmd
finish initial switch to new Moanin class

```{r}
n_genes = dim(y)[1]
indices = sample(1:dim(de_moanin_model)[1], n_genes, replace=TRUE)

@@

```{r bootstrapped_clustering, eval=FALSE}
# You may want to set the random seed of the experiment so that the results
# don't vary if you rerun the experiment.
# set.seed(random_seed)
n_genes = dim(de_moanin_model)[1] * sample_proportion
indices = sample(1:dim(de_moanin_model)[1], n_genes, replace=TRUE)

kmeans_clusters = splines_kmeans(de_moanin_model[indices,]
    n_clusters=n_clusters,
    random_seed=random_seed,
    n_init=20)

# Perform prediction on the whole set of data.
kmeans_clusters = splines_kmeans_predict(y, kmeans_clusters, method="distance")
```

>>>>

```{r}
n_genes = dim(de_moanin_model)[1]
indices = sample(1:dim(de_moanin_model)[1], n_genes, replace=TRUE)

@@

```{r bootstrapped_clustering, eval=FALSE}
# You may want to set the random seed of the experiment so that the results
# don't vary if you rerun the experiment.
# set.seed(random_seed)
n_genes = dim(de_moanin_model)[1] * subsample_proportion
indices = sample(1:dim(de_moanin_model)[1], n_genes, replace=TRUE)

kmeans_clusters = splines_kmeans(de_moanin_model[indices,],
    n_clusters=n_clusters,
    random_seed=random_seed,
    n_init=20)

# Perform prediction on the whole set of data.
kmeans_clusters = splines_kmeans_predict(de_moanin_model, kmeans_clusters, method="distance")
```
